Staged Abstract Interpreters

### 2019-06-15 paper/10_intro.tex
update

@@

@@

\paragraph{Futamura Projection of Abstract Interpreters}

@@

\paragraph{Abstraction without Regret}

>>>>

\iffalse
  Revision: 
  also motivate from the perspective that ADI is slow,
  analyze the reason: 1) interpretive overhead, 2) the use of monadic layers,
  3) the intrinsic complexity of abs int of HO language (ie CFA particularly).
  Then introduce the abstraction without regret.
  contribution: derive staged monad transformers.
\fi

@@

\rev{this power is based on the induction of natural number e}

@@

\paragraph{Intellectual Motivation: Futamura Projection of Abstract Interpreters}

@@

\paragraph{Practical Motivation: Abstraction without Regret}
\rev{Abstraction without performance regret; Performance without soundness regret}
